Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-22 doc/PRF2022/PRF_main.tex

@@

Figure~\ref{fig:s2esummary}(e)--(l) show the typical streamlines for JP
phases in background flow. Although the plots only show the region near
the JP phases, the fluid velocity $\uu$ and order parameter $u$ are
accounted for in all of $\mathbb{R}^2$. Moreover, $\uu$ satisfies the
rigid boundary condition at every JP-fluid interface i.e., the particles
interact with the local flow field and are not merely carried by
background flow.

@@

\subsection{Discussion}
We choose the range of shear rates $\dot \gamma \in [0, 0.02]$~ns$^{-1}$
by analyzing the capillary number of the JP phases. With this range,
there is a critical shear rate $\dot \gamma_*$ for the vesicle BL and
striated phases where shear stresses exceeded elastic stresses, leading
to rupture. The multilamellar phase did not rupture. By varying model
parameters, we perform a dimensional analysis on $\dot \gamma_*$.
Focusing on Type III JPs in shear flow, $\dot \gamma_* = 0.14$ ns$^{-1}$
for the basic model parameters (see
Section~\ref{sec:tunable_hydrophobicity}). Increasing and decreasing the
tension parameters $\gamma$ and $M$ by up to 10\% (collectively denoted
$\Delta \gamma/\gamma$) led to basically the same relative
increase/decrease in critical shear rate (denoted $\Delta \dot
\gamma_*/\dot \gamma_*$). This suggests that the critical shear rate
scales linearly with the tension parameters. Conversely, increasing
(resp.~decreasing) the length parameters $c$, $\rho$, and $\rho_0$ by up
to 10\% (collectively denoted $\Delta c/c$) leads to roughly twice the
relative decrease (resp.~increase) in the critical shear rate. This
points to an inverse-quadratic scaling in length.
Figure~\ref{fig:PramChange}(a) summarizes the findings and suggests the
scaling
\begin{equation}
\label{eq:CSR}
\mu \dot\gamma_* = K_{\text{III}} \frac{\gamma L}{c^2}.
\end{equation}
The scalar $K_{\text{III}}$ is specific to the striated phase under
shear flow. Here $L$ is the diameter of the phase sample, which is
proportional to $\gamma^*$ since the striated phase tends to cleave
during rupture (see Supplementary Movie S4). Our previous
work~\cite{Fu2022_JFM} found the scaling $\mu \dot\gamma_* =
K_{\text{I}} \gamma c^2/(\rho L^2)$ for a vesicle BL in shear flow.

The Results section showed that variations in free energy and strain
generally depend on the distribution of fluid stresses i.e., shear
versus TG flow. To further illustrate how fluid stresses interact with
the geometry of the JP phases, we initialize a circular vesicle bilayer
in various TG-flow cell sizes $\lambda$ ranging from $\lambda=1$ nm in
Figure~\ref{fig:PramChange}(b) to $\lambda=4$ nm in
Figure~\ref{fig:PramChange}(e). As shown in the Supplementary Material,
these JP vesicles fluctuate and deform around a steady shape of an
octagon ($\lambda=1$~nm), a dimpled square ($\lambda=2$~nm), a rounded
diamond ($\lambda=3$~nm), and a rounded rectangle ($\lambda=4$~nm).

>>>>

See Section~\ref{sec:movie_description} in the [Supplementary Material]
for movies showing the transition of 60 JPs that are initialized
randomly (inset of Figure~\ref{fig:relax}(a)) to the steady state
configurations (inset of Figures~\ref{fig:relax}(b), (d), and (e)).

@@

Figure~\ref{fig:s2esummary}(e)--(l) show the typical streamlines for JP
phases in background flow. Although the plots only show the region near
the JPs, the fluid velocity $\uu$ and order parameter $u$ are accounted
for in all of $\mathbb{R}^2$. Moreover, $\uu$ satisfies the rigid
boundary condition at every JP-fluid interface i.e., the particles
interact with the local flow field and are not merely carried by
background flow. See Section~\ref{sec:movie_description} in the
[Supplementary Material] for movies showing the dynamics of the JP
suspensions in Figure~\ref{fig:s2esummary}.

@@

\subsection{Discussion}
We choose the range of shear rates $\dot \gamma \in [0, 0.02]$~ns$^{-1}$
by analyzing the capillary number of the JP phases. With this range,
there is a critical shear rate $\dot \gamma_*$ for the vesicle BL and
striated phases where shear stresses exceeded elastic stresses, leading
to rupture. The multilamellar phase did not rupture. By varying model
parameters, we perform a dimensional analysis on $\dot \gamma_*$.
Focusing on Type III JPs in shear flow, $\dot \gamma_* = 0.14$ ns$^{-1}$
for the basic model parameters (see
Section~\ref{sec:tunable_hydrophobicity}). Increasing and decreasing the
tension parameters $\gamma$ and $M$ by up to 10\% (collectively denoted
$\Delta \gamma/\gamma$) led to basically the same relative
increase/decrease in critical shear rate (denoted $\Delta \dot
\gamma_*/\dot \gamma_*$). This suggests that the critical shear rate
scales linearly with the tension parameters. Conversely, increasing
(resp.~decreasing) the length parameters $c$, $\rho$, and $\rho_0$ by up
to 10\% (collectively denoted $\Delta c/c$) leads to roughly twice the
relative decrease (resp.~increase) in the critical shear rate. This
points to an inverse-quadratic scaling in length.
Figure~\ref{fig:PramChange}(a) summarizes the findings and suggests the
scaling
\begin{equation}
\label{eq:CSR}
\mu \dot\gamma_* = K_{\text{III}} \frac{\gamma L}{c^2}.
\end{equation}
The scalar $K_{\text{III}}$ is specific to the striated phase under
shear flow. Here $L$ is the diameter of the phase sample, which is
proportional to $\gamma^*$ since the striated phase tends to cleave
during rupture (see Supplementary movie). Our previous
work~\cite{Fu2022_JFM} found the scaling $\mu \dot\gamma_* =
K_{\text{I}} \gamma c^2/(\rho L^2)$ for a vesicle BL in shear flow.

The Results section showed that variations in free energy and strain
generally depend on the distribution of fluid stresses i.e., shear
versus TG flow. To further illustrate how fluid stresses interact with
the geometry of the JP phases, we initialize a circular vesicle bilayer
in various TG-flow cell sizes $\lambda$ ranging from $\lambda=1$ nm in
Figure~\ref{fig:PramChange}(b) to $\lambda=4$ nm in
Figure~\ref{fig:PramChange}(e).
%As shown in the Supplementary Material Movie S6,
These JP vesicles fluctuate and deform around a steady shape of an
octagon ($\lambda=1$~nm), a dimpled square ($\lambda=2$~nm), a rounded
diamond ($\lambda=3$~nm), and a rounded rectangle ($\lambda=4$~nm). See
Section~\ref{sec:movie_description} in the [Supplementary Material] for
a movie showing the dynamics of the JP vesicle for the four different
values of $\lambda$ in Figure~\ref{fig:PramChange}(b)--(e).
